Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
slow progress

First, parser generators typically parse inputs into an abstract syntax
tree (AST) that corresponds to the grammar.  In order to produce a data
structure that the rest of the application code can easily process,
application developers must write explicit {\em semantic actions} that
update the application's internal representation of the data based on
each AST node.  Writing these semantic actions by hand is error-prone,
much like other input processing code, and mistakes can result in memory
corruption bugs or misinterpreted inputs.

While it is possible to express short transformations on the input
entirely as semantic actions\footnote{This is in fact the design
rationale, to perform computation on the fly as the parser walks the
parse tree.}, more complicated programs usually construct an internal
representation, which contains all relevant information from the input
in a format native to the programming language used. For example, a C
programmer ideally wants to deal with structs and NULL-terminated arrays,
whereas a C++ programmer might expect STL containers, a Java programmer
interfaces, a Haskell programmer records and a LISP programmer property
lists.  The structure of this internal representation usually resembles
the structure of the grammar.

Therefore, a typical programmer has to describe the structure of his input
twice or even thrice to use a parser generator. Once, to write a grammar,
another time to write the semantic actions constructing his favourite
intermediate representation. In most languages the programmer also
has to write explicit type definitions, which describe the intermediate
object model again. Most programmers will baulk at this multiplication of
efforts and either hand-write a top-down parser which still eliminates
writing the semantic actions at the slight cost of verbosity or resort
to passing user input through their control flow, hopefully remembering
to verify each part before it is accessed.

>>>>

First, parser generators typically parse inputs into an abstract syntax
tree (AST) that corresponds to the grammar.  In order to produce a data
structure that the rest of the application code can easily process,
application developers must write explicit {\em semantic actions} that
update the application's internal representation of the data based on
each AST node.  Writing these semantic actions by hand is error-prone,
much like other input processing code, and mistakes can result in memory
corruption bugs or misinterpreted inputs.  Writing these semantic actions
also requires the programmer to describe the structure of the input three
times---once to describe the grammar, once to describe the internal data
structure, and once again in the semantic actions that translate the
grammar into the data structure---leading to another potential source
of bugs and inconsistencies.

### 2014-04-01 paper/relwk.tex
slow progress

>>>>

While it is possible to express short transformations on the input
entirely as semantic actions\footnote{This is in fact the design
rationale, to perform computation on the fly as the parser walks the
parse tree.}, more complicated programs usually construct an internal
representation, which contains all relevant information from the input
in a format native to the programming language used. For example, a C
programmer ideally wants to deal with structs and NULL-terminated arrays,
whereas a C++ programmer might expect STL containers, a Java programmer
interfaces, a Haskell programmer records and a LISP programmer property
lists.  The structure of this internal representation usually resembles
the structure of the grammar.
